---
title: "Weight of Fish"
author: "Jake Glickman"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

```{r}
All_Fish <- read.csv(file="Fish.csv")
```

```{r}
Perch <- filter(All_Fish, Species=="Perch")
```

```{r}
Perch <- select(Perch, -Species)
```

# Predicting Fish Weight



## Perch

```{r}
regsubsets.out <-
    regsubsets(Weight~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best model for Perch is Height and Width. This is shown because it is the one highest up on the y-axis.

### Best Two regressor model

The best two regressor model is Height and Width. The graph tells us it is the best 2 regressor model because it is the model places on the graph.


```{r}
Pike <- filter(All_Fish, Species=="Pike")
```

```{r}
Pike <- select(Pike, -Species)
```


## Pike

```{r}
regsubsets.out <-
    regsubsets(Weight~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best model is Length1, Length2, Length3, height, and width. This is because it has the highest adjusted r value, it is the one highest on the y-axis.

### Best Two regressor model

The best two regressor model is Length1 and Length3. This is because the graph tells us that it was the best in the 2 gregressor model, shown on the x-axis.


```{r}
Roach <- filter(All_Fish, Species=="Roach")
```

```{r}
Roach <- select(Roach, -Species)
```


## Roach

```{r}
regsubsets.out <-
    regsubsets(Weight~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best model is Length3 and Width because it has the highest adjusted r squared. It is the furthest upward on the y-axis.

### Best Two regressor model

The best two regressor model is Length3 and Width because it gave he highest adjusted r squared and the graph placed it as the best model regressor 2 model.

## Final Summary Statements

The best model for determining Perch fish weight is height and width. The best model for determining Pike fish weight is Length1, Length2, Length3, height, and width. The best model for determining Roach fish weight is Lenght3 and width.
